NTM CT Scoring - Initial Agreement

### 2023-04-03 Stacey Martiniano/ntm_agreement.qmd
Update ntm_agreement.qmd
some agreement code from Agresti

---
title: "NTM CT Scoring - Initial Agreement"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    code-fold: true
    toc: true
    toc-depth: 5
    toc-float: true
    self-contained: true
    fig-height: 8
    fig-width: 10
editor: visual
---

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
# Import data
api <- read.table("~/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
# Select relevant columns, convert to long data
data <- data %>%
  arrange(scan_id, scorer) %>%
  filter(scan_id > 2) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6)
data <- data %>%
  pivot_longer(bronchiectasis_rul:atelectasis___6,
    names_to = c("feature", "location"),
    names_pattern = "(.*)_(.*)$"
  ) %>%
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  )
data$location <- factor(data$location,
  levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", "lul", "rll", "rml", "rul"),
  labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
)
data$value <- factor(data$value, levels = c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose"))
vals <- levels(data$value)
# One column per scorer
data <- data %>% pivot_wider(names_from = scorer, values_from = value)
# Find disagreements
data$disagree <- !(data$AF == data$DL & data$DL == data$JW)
# Set colors for whole document
n <- length(vals)
name <- "Accent"
colors <- brewer.pal(n, name)
names(colors) <- vals
custom_colors <- scale_fill_manual(name = "", values = colors)
```

@@

```{r}
# Table
data %>%
  filter(disagree == T) %>%
  select(-disagree) %>%
  datatable(., rownames = F)
```
# Plots

>>>>

---
title: "NTM CT Scoring - Initial Agreement"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: source
---

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
# Import data
api <- read.table("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
# Select relevant columns, convert to long data
data <- data %>%
  arrange(scan_id, scorer) %>%
  filter(scan_id > 2) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6)
data <- data %>%
  pivot_longer(bronchiectasis_rul:atelectasis___6,
    names_to = c("feature", "location"),
    names_pattern = "(.*)_(.*)$"
  ) %>%
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  )
data$location <- factor(data$location,
  levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", "lul", "rll", "rml", "rul"),
  labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
)
data$value <- factor(data$value, levels = c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose"))
vals <- levels(data$value)
# One column per scorer
data <- data %>% pivot_wider(names_from = scorer, values_from = value)
# Find disagreements
data$disagree <- !(data$AF == data$DL & data$DL == data$JW)
# Set colors for whole document
n <- length(vals)
name <- "Accent"
colors <- brewer.pal(n, name)
names(colors) <- vals
custom_colors <- scale_fill_manual(name = "", values = colors)
```

```{r}
# Agresti examples
agt = matrix(c(22,2,2,0,
               5,7,14,0,
               0,2,36,0,
               0,1,17,10),
             byrow = T,ncol = 4)
dimnames(agt) = list("A"=1:4,"B"=1:4)
# As vectors
c1 = rep(1:4,times=diag(agt))
c1 = c(c1,rep(1:4,times=rowSums(agt*lower.tri(agt))))
c1 = c(c1,rep(1:4,times=rowSums(agt*upper.tri(agt))))
c2 = rep(1:4,times=diag(agt))
c2 = c(c2,rep(1:4,times=colSums(agt*lower.tri(agt))))
c2 = c(c2,rep(1:4,times=colSums(agt*upper.tri(agt))))
# Check
table(c1,c2)
# Data from Agresti Biometrics 1988
agt=matrix(c(1,1,22,1,2,2,1,3,2,1,4,0,1,5,0,
2,1,5,2,2,7,2,3,14,2,4,0,2,5,0,
3,1,0,3,2,2,3,3,36,3,4,0,3,5,0,
4,1,0,4,2,1,4,3,14,4,4,7,4,5,0,
5,1,0,5,2,0,5,3,3,5,4,0,5,5,3),byrow = T,ncol = 3)
```

@@

```{r}
# Table
data %>%
  filter(disagree == T) %>%
  select(-disagree) %>%
  datatable(., rownames = F)
```

# Plots
